Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes

### 2018-10-08 Ben_Manuscripts/structure_paper/supporting_information.tex
Responded to comments. Made axis labels bigger on plots.

@@

@@

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{cc}
  \toprule
  System & Diffusion Constant ($m^2/s$) \\ 
  \midrule
  Sandwiched, Ordered & $1.4 \times 10^{-14}$ \\
  Parallel Displaced, Ordered & $2.0 \times 10^{-14}$ \\
  Sandwiched, Disordered & $2.0 \times 10^{-14}$ \\
  Parallel Displaced, Disordered & $3.5 \times 10^{-14}$ \\
  \bottomrule
  \end{tabular}
  \caption{The diffusion constants for all systems are on the order of $10^{-14} m^2/s$ 
  .}~\label{table:msd}
  \end{table}

>>>>

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}

@@

  \section{Analysis scripts}\label{section:python_scripts}

@@

  \section{Monomer build procedure}\label{section:monomer_build_procedure}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
  \includegraphics[width=\linewidth]{monomer_diagonal.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.42\textwidth}
  \includegraphics[width=\linewidth]{stacked_monomers.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.35\textwidth}
  \includegraphics[width=\linewidth]{initial_pore.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
  \includegraphics[width=\linewidth]{initial_unit_cell.pdf}
  \caption{}
  \end{subfigure}
  %MRSF: I think this can be put in Supporting Information (we will get pushback to make this paper shorter, this is a good candidate)
  \caption{(a) We parameterized a single monomer and annealed it to produce a low-energy
		configuration. (b) We assembled monomers into columns by stacking them on top of each 
		other. (c) We duplicated each column and rotated them to create hydrophilic pore centers.
		We chose to stack twenty monomers into each column. (d) We duplicated the pores and 
		placed them into a monoclinic unit cell with hexagonal symmetry.}\label{fig:build_procedure}
  \end{figure}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{cc}
  \toprule
  System & Diffusion Constant ($m^2/s$) \\ 
  \midrule
  Sandwiched, Ordered & $1.4 \times 10^{-14}$ \\
  Parallel Displaced, Ordered & $2.0 \times 10^{-14}$ \\
  Sandwiched, Disordered & $2.0 \times 10^{-14}$ \\
  Parallel Displaced, Disordered & $3.5 \times 10^{-14}$ \\
  Parallel Displaced, 1 wt \% water & $7.1 \times 10^{-14}$ \\
  \bottomrule
  \end{tabular}
  \caption{The diffusion constants for all systems are on the order of $10^{-14} m^2/s$ 
  .}~\label{table:msd}
  \end{table}
